Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-22 paper/paper.tex
pass on example

Active reconnaissance is a method used by malicious individuals to
collect information about a computing system to determine potential
vulnerabilities. Active reconnaissance is a preliminary step towards
an actual attack. For example, Ping Scan is a very common type of
attack that scans the network for IPs of accessible hosts. An attacker
sends several ICMP Echo requests to a range of IP addresses in the
network and checks which ones respond to the requests. This allow the
attacker to know which machines are active in the network. Then (s)he
can choose one of them to attack.

\begin{figure}[h!]
  \vspace{1ex}
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{pingscan.suricata}
  \caption{Suricata rule for Ping Scan attack.}
  \label{fig:pingscan-example}
  \vspace{1ex}  
\end{figure}

Figure 4 shows a Suricata rule that captures a reproduction of a Ping
Scan attack available from NMAP~\cite{netmap}, a network discovery and
security auditing open-source tool. The relevant options are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

Again, to synthesize rules for a Ping Scan, \tname{} analyzes the
positive malicious traffic and extracts the following rule options:

@@

Again, note that rule \CodeIn{icode} was not present in the original
rule.  \tname{} produces the following five rules at the top of the
ranking after minimization and ranking.

>>>>

Active Reconnaissance is a method used by malicious individuals to
collect information about a computing system to determine potential
vulnerabilities. This methods is used as a preliminary step towards an
actual attack. For example, Ping Scan scans the network for IPs of
accessible hosts. An attacker sends several ICMP Echo requests to a
range of IP addresses in the network and checks which ones respond to
these requests. This method enables an attacker to know which machines
are active in the network.

\vspace{-2ex}
\begin{figure}[h!]
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{pingscan.suricata}
  \vspace{-2ex}    
  \caption{Suricata rule for Ping Scan attack.}
  \label{fig:pingscan-example}
\end{figure}
\vspace{-4ex}

Figure 4 shows a Suricata rule that captures a Ping Scan attempt, as
documented in NMAP~\cite{netmap}, a network discovery and security
auditing open-source tool. The relevant options are in bold---the
option \CodeIn{dsize: 0} indicates that the packet has no bytes in the
payload and the option \CodeIn{itype: 8} indicates that the packet to
be captured are ICMP Echo requests. Again, to synthesize rules for a
Ping Scan, \tname{} analyzes the positive malicious traffic and
extracts the following rule options:

@@

\noindent
Note that, although options \CodeIn{dsize:0} and \CodeIn{itype:8} are
present in the set of inferred options, the others are not.  This
indicates, as expected, that the set of rule options is
overspecified. \tname{} produces the following five rules at the top
of the ranking after minimization and ranking.\Mar{eu ainda estou
  aguardando isto. A tabela 3 tambem nao indica o resultado!}
